% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

\p{Dear Hiring Manager,}
\p{I am writing to express my strong interest in the IT Application Support - Intern position at your organization, as posted on \href{https://www.linkedin.com/jobs/view/it-application-support-intern-at-chubb-3804522468/}{LinkedIn}. Working toward my Bachelor degree in Information Technology and a solid foundation in technical IT knowledge, I am confident in my ability to effectively troubleshooting and maintaining IT applications and systems.}
\p{In my current role as a technology enthusiast and a dedicated IT professional, I have gained valuable experience in developing applications using Python, JavaScript, PHP, C/C++, MySQL, and MongoDB. My proficiency in analyzing user requirements, preparing technical specifications, and conducting thorough system tests aligns well with the key responsibilities outlined for the role. My education and experience at RMIT University Vietnam is focused intensively not only on technical knowledge, but also on project management processes, communication with stakeholders, as well as software quality assurance and user-centered software design.}
\p{As a proactive team player, I have a track record of timely notifying managers about potential application problems and escalating issues for further guidance or support. Being dedicated, hardworking, and resourceful, I possess the ability to work independently and creatively when problem solving.}
\p{My educational background and experience align with the qualifications you are seeking, and I am confident in my ability to make meaningful contributions to your team. Additionally, my proficiency in Linux, Git, and experience in open source software development prepared me to be a well-rounded candidate for this role.}
\p{I am excited about the opportunity to bring my technical knowledge, problem-solving skills, and dedication to the this role at your organization.}
\p{Thank you for considering my application. I look forward to the possibility of discussing how my skills and experiences match your team's needs in more detail.}
\p{Sincerely,\\
Tuong-Minh (Mike) Vo}

\end{document}
% ============================================== %

