% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\header}{
    \small{
        Tuong-Minh (Mike) Vo\\
        Ho Chi Minh City, Vietnam\\
        (+84)-385-892-705\\
        \href{miketvo@outlook.com}{miketvo@outlook.com}
    }
    \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

\header

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo, and I'm interested in applying for the Python Developer Intern position at Bosch Group. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence and Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Machine Learning, Practical Data Science, and Mathematics all focused on utilizing the Python ecosystem. Through these academic experience, I have gained a deep understanding of the software development lifecycle, QA/QC testing, and the importance of software documentation.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from web-based game to open-source software and web development. One notable achievement is my Python-based open-source image deduplicator application - Imdupes. Based on thorough research on image hashing, I have developed and optimized a custom image hashing algorithm that utilizes both traditional perceptual hashing techniques and color histogram sensitive enough to detect differences in images with or without transparency and with only minor differences. This has strengthen my skill to work both independently and in an international team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing to and learning from Bosch Group.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}

\end{document}
% ============================================== %
