% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\header}{
    \small{
        Tuong-Minh (Mike) Vo\\
        Ho Chi Minh City, Vietnam\\
        (+84)-385-892-705\\
        \href{miketvo@outlook.com}{miketvo@outlook.com}
    }
    \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

\header

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo, and I'm interested in applying for the Intern position with the Southeast Asia Research Team at Boston Consulting Group (BCG). Currently pursuing a Bachelor degree in Information Technology with specialization on Artificial Intelligence at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Machine Learning, Practical Data Science, and Software Engineering Project Management. Through these academic experience, I have gained strong analytical and research skill, along with a keen attention to detail. I am constantly striving to improve and learn more about new developments in data analysis and modelling, and my eager-to-learn outlook allows me to learn and develop throughout my academic and professional career.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from machine learning classification and recommendation system to open-source software and web development. One notable achievement is my contribution to the development of two Open Source Vietnamese Keyboards for the Keyman Input Method Editor. Through collaboration with Keyman developers, managers, and the user community via GitHub, I developed, tested, deployed, and maintained two keyboards implementing the two popular Vietnamese Telex and VNI keyboard input schemes. Both keyboard versions combined achieved significant traction with over 35,000 downloads on the Keyman website as of 2024, making a tangible impact in the Keyman open-source community. This has strengthen my skill to work both independently and in a collaborative team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing to and learning from the BCG Southeast Asia Research Team.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}

\end{document}
% ============================================== %
