% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\coverLetterHeader}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Mobile: (84)-385-892-705\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology in Artificial Intelligence; GPA: 3.50}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd

% ----- RELEVANT COURSEWORK -----
\section{Relevant Coursework}
  Artificial Intelligence,
  Machine Learning,
  Practical Data Science,
  Data Structures and Algorithms,
  Software Engineering Design,
  Computing Theory,
  Calculus I,
  Fullstack Development,
  Database Application
%

% ----- PROJECTS -----
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Imdupes}{}
      {Open-source versatile image deduplicator inspired by fdupes $|$ \href{https://github.com/miketvo/imdupes}{\faGithub\space miketvo/imdupes}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, PyInstaller, Pillow, NumPy, Python unittest}
        \resumeItem{Innovative Perceptual Hashing}
          {Developed a novel high-performance and efficient in-house image hashing algorithm that utilizes both traditional perceptual hashing techniques combined with color histogram analysis, which has never been done before.}
        \resumeItem{Deployment}
          {Deployed the application on Homebrew and Scoop package managers for cross-platform installation process on MacOS, Linux, and Windows.}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{}
      {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://github.com/miketvo/vn-kmn-compiler}{\faGithub\space miketvo/vn-kmn-compiler} $|$ \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keyman Keyboard Language}
        \resumeItem{Exhaustive Vietnamese Keystrokes Generator}
          {Utilized Python scripting to generate exhaustive syllable-based Telex and VNI keystrokes configurations from automated analysis and extraction of Vietnamese dictionaries. Related project: \href{https://github.com/miketvo/rime-ime-han-nom-data}{\faGithub\space Telex based Han Nom input method schema generator}.}
        \resumeItem{Open-source Collaboration}
          {Worked with Keyman developers and user community on keyboard deployment.}
        \resumeItem{Deployment}
          {Both Telex and VNI versions combined has over 35.000 downloads in total on Keyman website.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Sepsis Prediction Model}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment1}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment1} $|$ \href{https://www.kaggle.com/datasets/chaunguynnghunh/sepsis/}{\faDatabase\space Dataset: Kaggle - chaunguynnghunh/sepsis}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Scikit-Learn, Pandas, Seaborn}
        \resumeItem{F1 Score}
          {Achieved a $F_1$ score of 0.86 using a customized Bagged Tree model and robust data cleaning and preprocessing pipeline.}
        \resumeItem{Research Writing}
          {Produced a high quality research paper on the dataset and models used for sepsis prediction as part of the assignment.}
      \resumeItemListEnd

    \resumeSubheading
      {Flower Classification and Recommendation System}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment2}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment2} $|$ \href{https://www.kaggle.com/datasets/miketvo/rmit-flowers/}{\faDatabase\space Dataset: Kaggle - miketvo/rmit-flowers}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keras, Tensorflow, Scikit-Learn, Pillow}
        \resumeItem{Model Development and Deployment}
          {Developed an in-house CNN solution for feature extraction and a robust flower image classification and recommendation pipeline with an accuracy score of 0.7.}
        \resumeItem{Leadership}
          {Led student research team to produce a high-quality research paper on the subject matter.}
      \resumeItemListEnd

    \resumeSubheading
      {DsvCol}{}
      {Open-source cross-platform CLI-application pretty-printing delimiter separated value files $|$ \href{https://github.com/miketvo/dsvcol}{\faGithub\space miketvo/dsvcol}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {C, CMake, Bash, PowerShell}
      \resumeItemListEnd

    \resumeSubheading
      {Online Client Portfolio}{}
      {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {JavaScript, Gatsby, PostCSS}
        \resumeItem{UI/UX Design}
          {Worked remotely with the client to design and develop a user-friendly and brand-concious UI/UX using Agile project managament methodologies.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {Python, SQL, Java, C/C++, JavaScript, PHP, HTML/CSS, Lua, Bash, Batch, Powershell, TeX}
    \resumeSubItem{Technologies}
      {BeautifulSoup, Tensorflow, Pandas, React, NextJS, Vite, FastAPI, ExpressJS, MongoDB, MySQL}
    \resumeSubItem{Tools}
      {Jira, Git, Vim, VS Code, Linux (Ubuntu \& Arch Linux), Jupyter Lab/Notebook, Jetbrains IDEs, Excel}
    \resumeSubItem{Languages}
      {Vietnamese (Native), English (Bilingual)}
  \resumeSubHeadingListEnd
%

\newpage

% ----- COVER LETTER -----
\coverLetterHeader

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo, and I'm interested in applying for the Python Developer Remote Internship position at Winged Recruitment. Currently pursuing a Bachelor degree in Information Technology with specialization on Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your organization.}

\p{In my academic journey, I have gained a solid foundation in Machine Learning, Practical Data Science, and Mathematics all focused on utilizing the Python ecosystem. Through these academic experience, I have gained a deep understanding of the software development lifecycle, QA/QC testing, and the importance of software documentation.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from web-based game to open-source software and web development. One notable achievement is my Python-based open-source image deduplicator application - Imdupes. Based on thorough research on image hashing, I have developed and optimized a custom image hashing algorithm that utilizes both traditional perceptual hashing techniques and color histogram sensitive enough to detect differences in images with or without transparency and with only minor differences. This has strengthen my skill to work both independently and in an international team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing to and learning at Winged Recruitment.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
