% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=10mm}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-8pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\coverLetterHeader}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Mobile: (84)-385-892-705\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology in Artificial Intelligence; GPA: 3.50}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Vietnamese (Native), English (Bilingual)}
    \resumeSubItem{Softwares}
      {Microsoft Word, Microsoft Excel, Outlook Form, Google Docs, Audacity, Studio One, Adobe Illustrator, Adobe Lightroom, Adobe Photoshop, Adobe Premiere, Adobe After Effects}
    \resumeSubItem{Hardwares}
      {Boss Katana Amplifier, Behringer U-Phoria UM2 Audio Interface, Novation LaunchKey Mini, Zoom G1Xon Multi-Effects Processor, Zoom H1n Handheld Recorder, Takstar PC K200 Microphone, Electric Guitars}
    \resumeSubItem{Other Skills}
      {Soldering, Arduino, Software Engineering, Web Development, Web Scraping, Computer Automation, Data Analytics, Computer Science, Mathematics, Game Development, Research Writing, Video Editing, Audio Engineering, Music Theory, Piano, Guitar}      
  \resumeSubHeadingListEnd
%

% ----- AUDIO-VISUAL PROOJECTS -----
\section{Audio-Visual Projects}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Music Video - Summer Vibes}{}
    {\href{https://youtu.be/CHeXbIgzU5g}{\faYoutube\space https://youtu.be/CHeXbIgzU5g}}{}
    \resumeItemListStart
      \resumeItem{Song Writing and Music Production}
        {Worked as the composer and sound engineer for the original music piece. Drums, sound effects, electric guitar and MIDI recording with using Studio One.}
      \resumeItem{Video Editing}
        {Worked with Adobe Premiere to produce the music video.} 
    \resumeItemListEnd

    \resumeSubheading
      {Travel Video - Ba Ria Vung Tau Spring 2023 Montage}{}
      {\href{https://youtu.be/pGCyLukF0p8}{\faGlobe\space https://youtu.be/pGCyLukF0p8}}{}
      \resumeItemListStart
        \resumeItem{Sound Engineering}
          {Audio hardware setup and software post-processing for motorcycle and scenery sound recording.}
        \resumeItem{Video Editing}
          {Worked with Adobe Premiere to produce the travel video.} 
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- IT PROOJECTS -----
\section{Information Technology and Computer Science Projects}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Full-stack E-commerce Web Application (React/Node/RDBMS/NoSQL)}{}
    {\href{https://github.com/miketvo/rmit-isys2099-group9-app}{\faGithub\space miketvo/rmit-isys2099-group9-app}}{}
    \resumeItemListStart
      \resumeItem{Languages and Frameworks}
        {NodeJS, Express, Mongoose, Vite, React, Bootstrap, Axios, MySQL, MongoDB}
      \resumeItem{Leadership}
        {Utilize Agile methodology to lead a team of student of multiple specializations.}
      \resumeItem{Database Design}
        {Worked as the lead relational database architect to help deploy and integrate the application database with the backend server and the frontend using REST API.} 
    \resumeItemListEnd

    \resumeSubheading
      {Online Client Portfolio}{}
      {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {JavaScript, Gatsby, PostCSS}
        \resumeItem{UI/UX Design}
          {Worked remotely with the client to Designe and develop a user-friendly, responsive, and brand-conscious portfolio landing page.}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{}
      {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://github.com/miketvo/vn-kmn-compiler}{\faGithub\space miketvo/vn-kmn-compiler} $|$ \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keyman Keyboard Language}
        \resumeItem{Exhaustive Vietnamese Keystrokes Generator}
          {Utilized Python scripting to generate exhaustive syllable-based Telex and VNI keystrokes configurations from dictionary of Vietnamese words. Related project: \href{https://github.com/miketvo/rime-ime-han-nom-data}{\faGithub\space Telex based Han Nom input method schema generator}.}
        \resumeItem{Open-source Collaboration}
          {Worked with Keyman developers and user community on keyboard deployment.}
        \resumeItem{Deployment}
          {Both Telex and VNI versions combined has over 35.000 downloads in total on Keyman website.}
      \resumeItemListEnd

    \resumeSubheading
      {Sepsis Prediction Model}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment1}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment1} $|$ \href{https://www.kaggle.com/datasets/chaunguynnghunh/sepsis/}{\faDatabase\space Dataset: Kaggle - chaunguynnghunh/sepsis}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Scikit-Learn, Pandas, Seaborn}
        \resumeItem{F1 Score}
          {Achieved a $F_1$ score of 0.86 using a customized Bagged Tree model and robust data cleaning and preprocessing pipeline.}
        \resumeItem{Research Writing}
          {Produced a high quality research paper on the dataset and models used for sepsis prediction as part of the assignment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

\newpage

% ----- COVER LETTER -----
\coverLetterHeader

\p{\today}

\p{Dear RMIT (SGS) – Employment Team,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Technical Assistant (Part-time) position at RMIT University - The Business School. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and with hobbies in video production and audio engineering, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{Through my academic journey, I have gained a solid foundation in Information Technology, with expert knowledge in Microsoft Office products and Google Docs. Furthermore, the constant changes in the IT world prepared my ability to adapt to any tool and software that I need to use. I also have experience with audio-visual equipments from producing my own music and videos on YouTube, in addition to basic soldering skill necessary for basic maintenance of my AV equipment and occasional breadboarding with Arduino.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from e-commerce web application to music video production. One notable achievement is my contribution to the Full-stack E-commerce Web Application project for my Database Application course at RMIT University Vietnam, in which I worked as the program manager, SCRUM Master, and lead database architect, aiding my team in timely releases of deliverable for each sprint, communication with the stakeholders, and supervision of the integration of our database, backend, and frontend. This has strengthen my skill to work both independently and in a collaborative team environment with a strong focus on independent initiative, critical thinking, adaptability, and independent problem-solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing and learning in this role.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
