% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\header}{
    \small{
        Tuong-Minh (Mike) Vo\\
        Ho Chi Minh City, Vietnam\\
        (+84)-385-892-705\\
        \href{miketvo@outlook.com}{miketvo@outlook.com}
    }
    \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

\header

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Front-End Developer position at Dikshatek Vietnam. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Web Development, Machine Learning, and Practical Data Science. Through these academic experience, I have gained a deep understanding of the software development lifecycle, QA/QC testing, and the importance of software documentation. Furthermore, combined with my experience aiding in content writing and Search Engine Optimization (SEO) for my family online business in the past, I am confident in my ability to research the market and leverage my technical knowledges to contribute practical solutions for your team.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from web-based game to open-source software and web development. One notable achievement is my contribution to the development of two Open Source Vietnamese Keyboards for the Keyman Input Method Editor. Through collaboration with Keyman developers, managers, and the user community via GitHub, I developed, tested, deployed, and maintained two keyboards implementing the two popular Vietnamese Telex and VNI keyboard input schemes. Both keyboard versions combined achieved significant traction with over 35,000 downloads on the Keyman website as of 2024, making a tangible impact in the Keyman open-source community. This has strengthen my skill to work both independently and in an international team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing to and learning from Dikshatek Vietnam.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}

\end{document}
% ============================================== %
