% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=6mm}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-10pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItemHeading}[1]{\item\small{\textbf{#1:}}\vspace{-1.6pt}}
\newcommand{\resumeItemPlain}[1]{
  \setstretch{0.96}
  \item\small{
    {#1 \vspace{-1pt}}
  }
  \setstretch{1.0}
}
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{$-$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=16pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\resumeSubItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubItemListEnd}{\end{itemize}\vspace{-2pt}}
\newcommand{\coverLetterHeader}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Ho Chi Minh City, Vietnam\\
  Automation Intern & Mobile: (+84)-385-892-705\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology in Artificial Intelligence; GPA: 3.50/4.00}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00/4.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd

% ----- RELEVANT COURSEWORK -----
\section{Relevant Coursework}
  Machine Learning,
  Practical Data Science,
  Data Structures and Algorithms,
  Computing Theory,
  Artificial Intelligence,
  Fullstack Development,
  Database Application,
  Software Engineering Project Management
%

% ----- PROJECTS -----
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full-stack E-commerce Web Application (React/Node/RDBMS/NoSQL)}{Aug. - Sep. 2023}
      {\href{https://github.com/miketvo/rmit-isys2099-group9-app}{\faGithub\space miketvo/rmit-isys2099-group9-app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {NodeJS, Express, Mongoose, Vite, React, Bootstrap, Axios, MySQL, MongoDB}
        \resumeItemHeading{Responsibilities}
          \resumeSubItemListStart
            \resumeItemPlain
              {Led the project as the Project Lead and SCRUM Master, coordinating and executing the project timeline.}
            \resumeItemPlain
              {Served as the lead database architect for the project's relational and NoSQL databases.}
          \resumeSubItemListEnd
        \resumeItemHeading{Achievements}
          \resumeSubItemListStart
            \resumeItemPlain
              {Utilized Agile and SCRUM methodologies to lead and enable a team of student of multiple specializations to deliver the project delivarables in a timely manner for each sprint while preventing scope creep and managing project risks.}
            \resumeItemPlain
              {Successfully deployed and integrated the application's MySQL and MongoDB databases with its backend and frontend components using REST API.}
          \resumeSubItemListEnd
      \resumeItemListEnd

    \resumeSubheading
      {Flower Classification and Recommendation System}{May - Jun. 2023}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment2}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment2} $|$ \href{https://www.kaggle.com/datasets/miketvo/rmit-flowers/}{\faDatabase\space Dataset: Kaggle - miketvo/rmit-flowers}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keras, Tensorflow, Scikit-Learn, Pillow}
          \resumeItem{Responsibilities}
            {Led student research team to produce a high-quality research paper on the subject matter.}
          \resumeItem{Achievements}
            {Produced a robust in-house convolutional neural network solution for flower image classification and recommendation pipeline ready for deployment with an accuracy score of 0.7.}
      \resumeItemListEnd

    \resumeSubheading
      {Sepsis Prediction Model}{Apr. - May 2023}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment1}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment1} $|$ \href{https://www.kaggle.com/datasets/chaunguynnghunh/sepsis/}{\faDatabase\space Dataset: Kaggle - chaunguynnghunh/sepsis}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Scikit-Learn, Pandas, Seaborn}
        \resumeItem{Responsibilities}
          {Served as the solo data scientist and researcher for the assignment project.}
        \resumeItemHeading{Achievements}
          \resumeSubItemListStart
            \resumeItemPlain
              {Achieved a $F_1$ score of 0.86 using the Bagged Tree algorithm and implementing a robust data cleaning and preprocessing pipeline.}
            \resumeItemPlain
              {Produced a high-quality research paper on the dataset and models used for sepsis prediction.}
          \resumeSubItemListEnd
      \resumeItemListEnd
  
      \resumeSubheading
        {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{Feb. 2022 - Feb. 2023}
        {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://github.com/miketvo/vn-kmn-compiler}{\faGithub\space miketvo/vn-kmn-compiler}}{}
        \resumeItemListStart
          \resumeItem{Languages and Frameworks}
            {Python, Keyman Keyboard Language}
          \resumeItem{Responsibilities}
            {Worked with Keyman administrators, developers, and its user community on keyboard development, maintenance, and deployment within an international open-sourced collaborative environment.}
          \resumeItemHeading{Achievements}
            \resumeSubItemListStart
              \resumeItemPlain
                {Developed Python scripts to generate exhaustive syllable-based Telex and VNI keystrokes configurations by automatically analyzing and extracting data from Vietnamese dictionaries. Related project: \href{https://github.com/miketvo/rime-ime-han-nom-data}{\faGithub\space Telex based Han Nom input method schema generator}.}
              \resumeItemPlain
                {Both Telex and VNI keyboard versions combined has over 35.000 accumulative downloads on Keyman website as of 2024: \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}.}
            \resumeSubItemListEnd
      \resumeItemListEnd

      \resumeSubheading
        {Online Client Portfolio}{Jun. - Jul. 2021}
        {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
        \resumeItemListStart
          \resumeItem{Languages and Frameworks}
            {JavaScript, Gatsby, PostCSS}
          \resumeItem{Responsibilities}
            {Worked remotely with the client to design and develop a brand-conscious, user-friendly, and responsive portfolio landing page.}
          \resumeItem{Achievements}
            {Developed an interactive and attractive online portfolio to showcase the client's teaching experience, hosted using a distributed CDN and registered to a unique domain name for nearly 2 years.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {Python, SQL, Java, C/C++, JavaScript, PHP, HTML/CSS, Lua, Bash, Batch, Powershell, TeX}
    \resumeSubItem{Technologies}
      {Tensorflow, Keras, Pillow, Scikit-Learn, Pandas, React, Gatsby, NextJS, Vite, Express, MongoDB, MySQL}
    \resumeSubItem{Tools}
      {Jira, GitHub, BitBucket, Git, Vim, VS Code, Linux, Jupyter Lab/Notebook, Jetbrains IDEs, Figma, Illustrator}
    \resumeSubItem{Languages}
      {Vietnamese (Native), English (Bilingual)}
  \resumeSubHeadingListEnd
%

\newpage

% ----- COVER LETTER -----
\coverLetterHeader

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Automation Intern position at Avery Dennison RBIS Vietnam. Currently pursuing a Bachelor's degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your organization.}

\p{In my academic journey, I have gained a solid foundation in Machine Learning, Practical Data Science, and Artificial Intelligence. Through this academic experience, I have gained strong analytical and research skills, along with a keen attention to detail. Although I currently do not have much experience with time series forecasting using ARIMA \& SARIMA models, I am constantly striving to improve and learn more about new developments in data analysis and modelling, and my eager-to-learn outlook allows me to quickly learn, adapt, and develop throughout my academic and professional career.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from machine learning classification and recommendation system to open-source software and web development. One notable achievement is my work on the Flower Classification and Recommendation System course project at RMIT University Vietnam, where I worked as the lead researcher and machine learning specialist of my team, utilizing convolutional neural network and deep learning to achieve a good performance result on our flower classification model. This has strengthen my skill to work both independently and in a collaborative team environment, with a strong focus on the data science knowledge of data analysis, classification algorithms, and clustering algorithms.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing to and learning at Avery Dennison RBIS Vietnam.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
