% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=8mm}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-8pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\coverLetterHeader}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Mobile: (84)-385-892-705\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology in Artificial Intelligence; GPA: 3.50}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd

% ----- RELEVANT COURSEWORK -----
\section{Relevent Coursework}
  Fullstack Development,
  Web Development,
  Database Application,
  Machine Learning,
  Practical Data Science,
  Data Structures and Algorithms,
  Computing Theory,
  Artificial Intelligence,
  Software Engineering Design
%

% ----- PROOJECTS -----
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{}
      {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://github.com/miketvo/vn-kmn-compiler}{\faGithub\space miketvo/vn-kmn-compiler} $|$ \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keyman Keyboard Language}
        \resumeItem{Exhaustive Vietnamese Keystrokes Generator}
          {Utilized Python scripting to generate exhaustive syllable-based Telex and VNI keystrokes configurations from dictionary of Vietnamese words. Related project: \href{https://github.com/miketvo/rime-ime-han-nom-data}{\faGithub\space Telex based Han Nom input method schema generator}.}
        \resumeItem{Open-source Collaboration}
          {Worked with Keyman developers and user community on keyboard deployment.}
        \resumeItem{Deployment}
          {Both Telex and VNI versions combined has over 35.000 downloads in total on Keyman website.}
      \resumeItemListEnd

    \resumeSubheading
      {Imdupes}{}
      {Open-source versatile image deduplicator inspired by fdupes $|$ \href{https://github.com/miketvo/imdupes}{\faGithub\space miketvo/imdupes}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, PyInstaller, Pillow, NumPy, Python unittest}
        \resumeItem{Innovative Perceptual Hashing}
          {Developed a high-performance and efficient in-house image hashing algorithm that utilizes both traditional perceptual hashing techniques and color histogram.}
        \resumeItem{Deployment}
          {Deployed the application on Homebrew and Scoop package managers for cross-platform installation process on MacOS, Linux, and Windows.}
      \resumeItemListEnd

    \resumeSubheading
      {Sepsis Prediction Model}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment1}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment1} $|$ \href{https://www.kaggle.com/datasets/chaunguynnghunh/sepsis/}{\faDatabase\space Dataset: Kaggle - chaunguynnghunh/sepsis}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Scikit-Learn, Pandas, Seaborn}
        \resumeItem{F1 Score}
          {Achieved a $F_1$ score of 0.86 using a customized Bagged Tree model and robust data processing pipeline.}
      \resumeItemListEnd

    \resumeSubheading
      {DsvCol}{}
      {Open-source cross-platform CLI-application pretty-printing delimiter separated value files $|$ \href{https://github.com/miketvo/dsvcol}{\faGithub\space miketvo/dsvcol}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {C, CMake, Bash, PowerShell}
        \resumeItem{Cross-platform Build Support}
          {Developed cross-platform build system for both Linux and Windows using CMake.}
      \resumeItemListEnd

    \resumeSubheading
      {Online Client Portfolio}{}
      {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {JavaScript, Gatsby, PostCSS}
        \resumeItem{UI/UX Design}
          {Worked remotely with the client to Designe and develop a user-friendly, responsive, and brand-conscious portfolio landing page.}
      \resumeItemListEnd

    \resumeSubheading
      {Full-stack E-commerce Web Application}{}
      {\href{https://github.com/miketvo/rmit-isys2099-group9-app}{\faGithub\space miketvo/rmit-isys2099-group9-app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {NodeJS, Express, Mongoose, Vite, ReactJS, Bootstrap, Axios, MySQL, MongoDB}
        \resumeItem{Leadership}
          {Utilize Agile methodology to lead a team of student of multiple specializations.}
        \resumeItem{Database Design}
          {Worked as the lead relational database designer to help deploy the application database.} 
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {Python, SQL, Java, C/C++, JavaScript, PHP, HTML/CSS, Lua, Bash, Batch, Powershell, TeX}
    \resumeSubItem{Technologies}
      {ReactJS, GatsbyJS, NextJS, Vite, ExpressJS, MySQL, MongoDB, JUnit, Tensorflow, Keras, Pandas}
    \resumeSubItem{Tools}
      {Jira, Git, Vim, Visual Studio Code, Linux (Ubuntu \& Arch Linux), Jupyter Lab/Notebook, Jetbrains IDEs}
    \resumeSubItem{Languages}
      {Vietnamese (Native), English (Bilingual)}
  \resumeSubHeadingListEnd
%

% ----- COVER LETTER -----
\coverLetterHeader

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Information Technology Intern (posted on your website as Technology Development Internship) position at AH-GlobalGroup. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Full-stack Web Development, Machine Learning, and Practical Data Science. Through these academic experience, I have gained a deep understanding of the software development lifecycle, deployment, and the importance of software documentation and software engineering project management processes. Furthermore, through my academic and personal project, I have accumulated extensive working experience with Ubuntu and Arch Linux setting up toolchains, build systems, and automated scripts on these environment.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from web-based game to open-source software and web development. One notable achievement is my contribution to the development of two Open Source Vietnamese Keyboards for the Keyman Input Method Editor. Through collaboration with Keyman developers, managers, and the user community via GitHub, I developed, tested, deployed, and maintained two keyboards implementing the two popular Vietnamese Telex and VNI keyboard input schemes. Both keyboard versions combined achieved significant traction with over 35,000 downloads on the Keyman website as of 2024, making a tangible impact in the Keyman open-source community. This has strengthen my skill to work both independently and in an international team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity to contribute and learn at AH-GlobalGroup.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
