% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\header}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- COVER LETTER -----
\header

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Software Engineering Intern (C++) position at OPSWAT Vietnam. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Full-stack Web Development, Machine Learning, and Practical Data Science. Through these academic experience, I have gained a deep understanding of the software development lifecycle, deployment, and the importance of software documentation and software engineering project management processes. Furthermore, through my academic and personal projects, I have accumulated extensive working experience with MongoDB, MySQL, NodeJS, and building RESTful APIs and MVC. I believe my set of skills makes me a strong candidate for this position.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from e-commerce web application to open-source software and data science projects. One notable achievement is my contribution to the Full-stack E-commerce Web Application project for my Database Application course at RMIT University Vietnam, in which I worked as the program manager, SCRUM Master, and lead database architect, aiding my team in timely releases of deliverable for each sprint, communication with the stakeholders, and supervision of the integration of our database, backend, and frontend. This has strengthen my skill to work both independently and in an collaborative team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity to contribute and learn at OPSWAT Vietnam.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
