% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=8mm}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-8pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\coverLetterHeader}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Mobile: (84)-385-892-705\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology in Artificial Intelligence; GPA: 3.50}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd

% ----- RELEVANT COURSEWORK -----
\section{Relevent Coursework}
  Machine Learning,
  Practical Data Science,
  Database Application,
  Web Development,
  Fullstack Development,
  Data Structures and Algorithms,
  Computing Theory,
  Artificial Intelligence,
  Software Engineering Design
%

% ----- PROOJECTS -----
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sepsis Prediction Model}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment1}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment1} $|$ \href{https://www.kaggle.com/datasets/chaunguynnghunh/sepsis/}{\faDatabase\space Dataset: Kaggle - chaunguynnghunh/sepsis}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Scikit-Learn, Pandas, Seaborn}
        \resumeItem{F1 Score}
          {Achieved a $F_1$ score of 0.86 using a customized Bagged Tree model and robust data cleaning and preprocessing pipeline.}
        \resumeItem{Research Writing}
          {Produced a high quality research paper on the dataset and models used for sepsis prediction as part of the assignment.}
      \resumeItemListEnd

    \resumeSubheading
      {Flower Classification and Recommendation System}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment2}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment2} $|$ \href{https://www.kaggle.com/datasets/miketvo/rmit-flowers/}{\faDatabase\space Dataset: Kaggle - miketvo/rmit-flowers}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keras, Tensorflow, Scikit-Learn, Pillow}
        \resumeItem{Model Development and Deployment}
          {Developed an in-house CNN solution for feature extraction and a robust flower image classification and recommendation pipeline with an accuracy score of 0.7.}
        \resumeItem{Leadership}
          {Led student research team to produce a high-quality research paper on the subject matter.}
      \resumeItemListEnd

    \resumeSubheading
      {Full-stack E-commerce Web Application}{}
      {\href{https://github.com/miketvo/rmit-isys2099-group9-app}{\faGithub\space miketvo/rmit-isys2099-group9-app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {NodeJS, Express, Mongoose, Vite, ReactJS, Bootstrap, Axios, MySQL, MongoDB}
        \resumeItem{Leadership}
          {Utilize Agile methodology to lead a team of student of multiple specializations.}
        \resumeItem{Database Design}
          {Worked as the lead relational database architect to help deploy the application database.} 
      \resumeItemListEnd

    \resumeSubheading
      {Online Client Portfolio}{}
      {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {JavaScript, Gatsby, PostCSS}
        \resumeItem{UI/UX Design}
          {Worked remotely with the client to Designe and develop a user-friendly, responsive, and brand-conscious portfolio landing page.}
      \resumeItemListEnd

      \resumeSubheading
      {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{}
      {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://github.com/miketvo/vn-kmn-compiler}{\faGithub\space miketvo/vn-kmn-compiler} $|$ \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keyman Keyboard Language}
        \resumeItem{Exhaustive Vietnamese Keystrokes Generator}
          {Utilized Python scripting to generate exhaustive syllable-based Telex and VNI keystrokes configurations from automated analysis and extraction of Vietnamese dictionaries. Related project: \href{https://github.com/miketvo/rime-ime-han-nom-data}{\faGithub\space Telex based Han Nom input method schema generator}.}
        \resumeItem{Open-source Collaboration}
          {Worked with Keyman developers and user community on keyboard deployment.}
        \resumeItem{Deployment}
          {Both Telex and VNI versions combined has over 35.000 downloads in total on Keyman website.}
      \resumeItemListEnd

    \resumeSubheading
      {Imdupes}{}
      {Open-source versatile image deduplicator inspired by fdupes $|$ \href{https://github.com/miketvo/imdupes}{\faGithub\space miketvo/imdupes}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, PyInstaller, Pillow, NumPy, Python unittest}
        \resumeItem{Innovative Perceptual Hashing}
          {Developed a novel high-performance and efficient in-house image hashing algorithm that utilizes both traditional perceptual hashing techniques combined with color histogram analysis, which has never been done before.}
        \resumeItem{Deployment}
          {Deployed the application on Homebrew and Scoop package managers for cross-platform installation process on MacOS, Linux, and Windows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {Python, SQL, Java, C/C++, JavaScript, PHP, HTML/CSS, Lua, Bash, Batch, Powershell, VBA, TeX}
    \resumeSubItem{Technologies}
      {ReactJS, GatsbyJS, NextJS, Vite, ExpressJS, MySQL, MongoDB, JUnit, Tensorflow, Keras, Pandas}
    \resumeSubItem{Tools}
      {Jira, Git, Vim, VS Code, Linux (Ubuntu \& Arch Linux), Jupyter Lab/Notebook, Jetbrains IDEs, Excel}
    \resumeSubItem{Languages}
      {Vietnamese (Native), English (Bilingual)}
  \resumeSubHeadingListEnd
%

\newpage

% ----- SKILLS -----
\coverLetterHeader

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Business/Data Analyst Intern position at Rakuna. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Machine Learning, Practical Data Science, and Artificial Intelligence. Through these academic experience, I have gained strong analytical and research skill, along with a keen attention to detail. I am constantly striving to improve and learn more about new developments in data analysis and modelling, and my eager-to-learn outlook allows me to learn and develop throughout my academic and professional career. I am confident in my ability to adapt leverage my data science and machine learning knowledge to contribute practical solutions for your team.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from machine learning classification and recommendation system to open-source software and web development. One notable achievement is my work on the Flower Classification and Recommendation System course project at RMIT University Vietnam, where I worked as the lead researcher and machine learning specialist of my team, utilizing convolutional neural network and deep learning to achieve a good performance result on our flower classification model. This has strengthen my skill to work both independently and in a team environment, with a strong focus on the data science knowledge of data analysis, classification algorithms, and clustering algorithms.}

\p{Thank you for your time and consideration. I look forward to the opportunity of contributing to and learning at Rakuna.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
