% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-10pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumePlainItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

{Dear RMIT (SGS) – Employment Team,\\\vspace{6pt}}
{I am writing to express my interest in the Student Support Officer (Concierge) position at RMIT Connect, as posted on RMIT Careers Portal. I am Currently enrolled in the Bachelor of Information Technology program at RMIT University Vietnam, and I am excited about the opportunity to contribute to the excellent student services and support that your team provides.\\\vspace{6pt}}
{My strong commitment to delivering outstanding student services is evident through my volunteer experience at X-RUN 2023, where I worked as part of the Student Life Red Team. This role required effective communication and teamwork skills to ensure a safe and rewarding experience for participants. Furthermore, my past experience abroad volunteering for Teachers Appreciation Day 2016 also showcases my dedication to communicate and work with individuals of diverse cultural backgrounds.\\\vspace{6pt}}
{In my academic and professional pursuits, I have led teams in various projects, such as developing a browser game, leading a research team in the creation of a flower classification and recommendation system, working with a client to build an online portfolio, and working in an open-source software project. These experiences have honed my teamwork, leadership, and communication skills, which I believe align with the requirements of this position.\\\vspace{6pt}}
{I believe that the experience I would gain from this position resonates with my career aspirations. I am eager to leverage this opportunities to further develop my customer service skills and essential social skills desired by future employers, especially when working with clients and stakeholders in my field of study.\\\vspace{6pt}}
{I am confident that my academic background, volunteer experience, teamwork, and leadership skills make me a strong candidate for this position. I am excited about the prospect of contributing to the vibrant and diverse community at RMIT University and am enthusiastic about the chance to learn and grow in a high-volume, customer-focused environment.\\\vspace{6pt}}
{Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experiences align with the needs of your team.\\\vspace{6pt}}
{Sincerely,\\Tuong-Minh (Mike) Vo}

\pagebreak

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Mobile: (84)-385-892-705\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Infomation Technology in Artificial Intelligence; GPA: 3.50}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd

% ----- RELEVANT QUALIFICATIONS -----
\section{Relevant Qualifications}
  \resumeSubHeadingListStart
    \vspace{-14pt}
    \begin{multicols}{2}
      \resumeSubItem{SAT with Essay}
        {1870/2400}
      \resumeSubItem{TOEFL iBT}
        {110/120}
    \end{multicols}
  \resumeSubHeadingListEnd
%

% ----- VOLUNTEER EXPERIENCE -----
\section{Volunteer Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Volunteer}{June 2023}
    {X-RUN 2023}{Student Life Red Team, RMIT University Vietnam - Saigon South}
    \resumeItemListStart
      \resumePlainItem
        {Worked as volunteer for X-RUN 2023 - obstacle course sports event at RMIT University Vietnam, I provided the participants a safe and rewarding experience through the obstacle course, providing them with direction, safety guidance, and refreshments when needed.}
        \resumeItem{Skills}
          {Teamwork, Communication}
    \resumeItemListEnd

    \resumeSubheading
      {Event Assistant \& Performer}{November 2016}
      {Teachers Appreciation Day}{Vietnamese Student Association \& Music Club, Seattle Central College}
      \resumeItemListStart
        \resumePlainItem
          {Worked as a core member of both the Vietnamese Student Association and the Music Club at Seattle Central College to help plan and execute the successful event of Teachers Appreaciation Day 2016.}
          \resumeItem{Skills}
            {Teamwork, Public Speaking, Guitar, Live Performance}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- PROOJECTS -----
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Browser Game}{Team Leader, Designer}
      {\href{https://miketvo.github.io/404-page.html}{\faGlobe\space miketvo.github.io/404-page}}{}
      \resumeItemListStart
        \resumePlainItem
          {Helped lead my team develop a simple HTML game loaded onto the user's device whenever they encounter a 404 NOT FOUND error on my personal website. Repurposed from coursework project for COSC2083. Currently hosted using GitHub Pages.}
          \resumeItem{Skills}
            {Leadership, Programming, Graphic Design}
      \resumeItemListEnd

     \resumeSubheading
      {Online Client Portfolio}{Freelance Web Developer \& Designer}
      {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
      \resumeItemListStart
      \resumePlainItem{Worked remotely with the client to design and develop a user-friendly and brand-concious UI/UX using Agile project managament methodologies.}
      \resumeItem{Skills}
        {Communication, Customer Service, Programming, Graphic Design}
      \resumeItemListEnd

    \resumeSubheading
      {Flower Classification and Recommendation System}{Team Leader, Researcher}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment2}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment2} $|$ \href{https://www.kaggle.com/datasets/miketvo/rmit-flowers/}{\faDatabase\space Dataset: Kaggle - miketvo/rmit-flowers}}{}
      \resumeItemListStart
      \resumePlainItem{Developed an in-house CNN solution for feature extraction and a robust flower image classification and recommendation pipeline with an accuracy score of 0.7. Led student research team to produce a high-quality research paper on the subject matter.}
      \resumeItem{Skills}
        {Leadership, Communication, Research, Data Analytics, Programming}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{Software Engineer}
      {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}}{}
      \resumeItemListStart
        \resumePlainItem{Collaborated via GitHub with Keyman developers, managers, and user community to develop two successful Vietnamese IMEs - Vietnamese Telex and Vietnamese VNI. Both versions combined achieved over 34,000 downloads in total on Keyman website.}
        \resumeItem{Skills}
          {Communication, Programming, Software Engineering, Customer Service}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \vspace{-14pt}
    \begin{multicols}{3}
      \item\small{{Teamwork \vspace{-9pt}}}
      \item\small{{Communication \vspace{-9pt}}}
      \item\small{{Leadership \vspace{-9pt}}}
      \item\small{{Customer Service \vspace{-9pt}}}
      \item\small{{Programming \vspace{-9pt}}}
      \item\small{{Graphic Design \vspace{-9pt}}}
    \end{multicols}
  \resumeSubHeadingListEnd
%

\end{document}
% ============================================== %
