% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=12mm, includefoot}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
%

% ----- Custom commands -----
\newcommand{\header}{
    \small{
        Tuong-Minh (Mike) Vo\\
        Ho Chi Minh City, Vietnam\\
        (+84)-385-892-705\\
        \href{miketvo@outlook.com}{miketvo@outlook.com}
    }
    \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

\header

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Data Analyst position at Abbott Vietnam. Currently pursuing a Bachelor degree in Information Technology with specialization on Artificial Intelligence and Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your organization.}

\p{In my academic journey, I have gained a solid foundation in Machine Learning, Practical Data Science, and Artificial Intelligence. Through these academic experience, I have gained strong analytical and research skill, along with a keen attention to detail. I am constantly striving to improve and learn more about new developments in data analysis and modelling, and my eager-to-learn outlook allows me to learn and develop throughout my academic and professional career.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from machine learning classification and recommendation system to open-source software and web development. One notable achievement is my work on the Flower Classification and Recommendation System course project at RMIT University Vietnam, where I worked as the lead researcher and machine learning specialist of my team, utilizing convolutional neural network and deep learning to achieve a good performance result on our flower classification model. This has strengthen my skill to work both independently and in an international team environment, with a strong focus on the data science knowledge of data analysis, classification and clustering algorithms.}

\p{Thank you for your time and consideration for my application. I look forward to the opportunity of contributing to and learning at Abbott.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}

\end{document}
% ============================================== %
