% ============================================== %
%%%%%%%%%%%%%%%%%%%% PREAMBLE %%%%%%%%%%%%%%%%%%%%
% ============================================== %
\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage[usenames, dvipsnames]{color}

% ----- Sections formatting
\geometry{margin=10mm}
\pagestyle{empty}
\urlstyle{same}
\raggedbottom
\raggedright
\titleformat{\section}{\vspace{-8pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]
%

% ----- Custom commands -----
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}
\newcommand{\coverLetterHeader}{
  \small{
    Tuong-Minh (Mike) Vo\\
    Ho Chi Minh City, Vietnam\\
    (+84)-385-892-705\\
    \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}
  }
  \par\noindent\hrulefill
}
\newcommand{\p}[1]{#1\\\vspace{6pt}}
%
% ============================================== %


% ============================================== %
%%%%%%%%%%%%%%%%%%%%%% BODY %%%%%%%%%%%%%%%%%%%%%%
% ============================================== %
\begin{document}

% ----- HEADING -----
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Tuong-Minh (Mike) Vo} & Email: \href{mailto:miketvo@outlook.com}{miketvo@outlook.com}\\
  \href{https://github.com/miketvo}{\faGithub\space miketvo} $|$ \href{https://www.linkedin.com/in/miketvo/}{\faLinkedin\space miketvo} $|$ \href{https://miketvo.com/}{\faGlobe\space miketvo.com} & Mobile: (84)-385-892-705\\
\end{tabular*}
\hrule height 2pt
%

% ----- EDUCATION -----
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {RMIT University Vietnam}{Ho Chi Minh City, Vietnam}
      {Bachelor of Information Technology in Artificial Intelligence; GPA: 3.50}{Oct. 2020 -- Expected: Mar. 2025}
    \resumeSubheading
      {Seattle Central College}{Seattle, WA, United States}
      {Associate of Liberal Arts and Sciences; GPA: 3.00}{Sep. 2016 -- Aug. 2017}
  \resumeSubHeadingListEnd

% ----- RELEVANT COURSEWORK -----
\section{Relevent Coursework}
  Fullstack Development,
  Web Development,
  Database Application,
  Machine Learning,
  Practical Data Science,
  Data Structures and Algorithms,
  Computing Theory,
  Artificial Intelligence,
  Software Engineering Design
%

% ----- PROOJECTS -----
\section{Projects}
  \resumeSubHeadingListStart

  \resumeSubheading
    {Full-stack E-commerce Web Application}{}
    {\href{https://github.com/miketvo/rmit-isys2099-group9-app}{\faGithub\space miketvo/rmit-isys2099-group9-app}}{}
    \resumeItemListStart
      \resumeItem{Languages and Frameworks}
        {NodeJS, Express, Mongoose, Vite, React, Bootstrap, Axios, MySQL, MongoDB}
      \resumeItem{Leadership}
        {Utilize Agile methodology to lead a team of student of multiple specializations.}
      \resumeItem{Database Design}
        {Worked as the lead relational database architect to help deploy and integrate the application database with the backend server and the frontend using REST API.} 
    \resumeItemListEnd

    \resumeSubheading
      {Online Client Portfolio}{}
      {\href{https://duonghanhi.netlify.app/}{\faGlobe\space duonghanhi.netlify.app}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {JavaScript, Gatsby, PostCSS}
        \resumeItem{UI/UX Design}
          {Worked remotely with the client to Designe and develop a user-friendly, responsive, and brand-conscious portfolio landing page.}
      \resumeItemListEnd

    \resumeSubheading
      {Open Source Vietnamese Keyboard for Keyman Input Method Editor}{}
      {\href{https://github.com/miketvo/keyboards}{\faGithub\space miketvo/keyboards} $|$ \href{https://github.com/miketvo/vn-kmn-compiler}{\faGithub\space miketvo/vn-kmn-compiler} $|$ \href{https://keyman.com/keyboards/vietnamese_telex}{\faGlobe\space Keyman - Vietnamese Telex} $|$ \href{https://keyman.com/keyboards/vietnamese_vni}{\faGlobe\space Keyman - Vietnamese VNI}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Keyman Keyboard Language}
        \resumeItem{Exhaustive Vietnamese Keystrokes Generator}
          {Utilized Python scripting to generate exhaustive syllable-based Telex and VNI keystrokes configurations from dictionary of Vietnamese words. Related project: \href{https://github.com/miketvo/rime-ime-han-nom-data}{\faGithub\space Telex based Han Nom input method schema generator}.}
        \resumeItem{Open-source Collaboration}
          {Worked with Keyman developers and user community on keyboard deployment.}
        \resumeItem{Deployment}
          {Both Telex and VNI versions combined has over 35.000 downloads in total on Keyman website.}
      \resumeItemListEnd

    \resumeSubheading
      {Imdupes}{}
      {Open-source versatile image deduplicator inspired by fdupes $|$ \href{https://github.com/miketvo/imdupes}{\faGithub\space miketvo/imdupes}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, PyInstaller, Pillow, NumPy, Python unittest}
        \resumeItem{Innovative Perceptual Hashing}
          {Developed a high-performance and efficient in-house image hashing algorithm that utilizes both traditional perceptual hashing techniques and color histogram.}
        \resumeItem{Deployment}
          {Deployed the application on Homebrew and Scoop package managers for cross-platform installation process on MacOS, Linux, and Windows.}
      \resumeItemListEnd

    \resumeSubheading
      {DsvCol}{}
      {Open-source cross-platform CLI-application pretty-printing delimiter separated value files $|$ \href{https://github.com/miketvo/dsvcol}{\faGithub\space miketvo/dsvcol}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {C, CMake, Bash, PowerShell}
        \resumeItem{Cross-platform Build Support}
          {Developed cross-platform CMake build system for both Linux and Windows.}
      \resumeItemListEnd

    \resumeSubheading
      {Sepsis Prediction Model}{}
      {\href{https://github.com/miketvo/rmit2023a-cosc2753-assignment1}{\faGithub\space miketvo/rmit2023a-cosc2753-assignment1} $|$ \href{https://www.kaggle.com/datasets/chaunguynnghunh/sepsis/}{\faDatabase\space Dataset: Kaggle - chaunguynnghunh/sepsis}}{}
      \resumeItemListStart
        \resumeItem{Languages and Frameworks}
          {Python, Scikit-Learn, Pandas, Seaborn}
        \resumeItem{F1 Score}
          {Achieved a $F_1$ score of 0.86 using a customized Bagged Tree model and robust data cleaning and preprocessing pipeline.}
        \resumeItem{Research Writing}
          {Produced a high quality research paper on the dataset and models used for sepsis prediction as part of the assignment.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%

% ----- SKILLS -----
\section{Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming}
      {Python, JavaScript, SQL, Java, C/C++, HTML/CSS, Lua, Bash, Batch, Powershell, TeX}
    \resumeSubItem{Technologies}
      {ReactJS, GatsbyJS, NextJS, Vite, ExpressJS, FastAPI, MySQL, MongoDB, Tensorflow, Keras, Pandas}
    \resumeSubItem{Tools}
      {Jira, Git, Vim, Visual Studio Code, Postman, Linux, Jupyter Lab/Notebook, Jetbrains IDEs}
    \resumeSubItem{Languages}
      {Vietnamese (Native), English (Bilingual)}
  \resumeSubHeadingListEnd
%

\newpage

% ----- COVER LETTER -----
\coverLetterHeader

\p{\today}

\p{Dear Hiring Manager,}

\p{My name is Mike Vo. I am writing to express my interest in applying for the Software Developer, Intern - 48201BR position at Synopsys Vietnam. Currently pursuing a Bachelor degree in Information Technology with specialization in Artificial Intelligence \& Data Analytics at RMIT University Vietnam, and anticipating graduation in early 2025, I am excited about the opportunity to contribute my skills and enthusiasm to your team.}

\p{In my academic journey, I have gained a solid foundation in Full-stack Web Development, Machine Learning, and Practical Data Science. Through these academic experience, I have gained a deep understanding of the software development lifecycle, deployment, and the importance of software documentation and software engineering project management processes. Furthermore, through my academic and personal projects, I have accumulated extensive working experience with MongoDB, MySQL, NodeJS, and building RESTful APIs. I believe my set of skills makes me a strong candidate for this position.}

\p{As a proactive learner and team player, I have successfully completed various projects, ranging from e-commerce web application to open-source software and data science projects. One notable achievement is my contribution to the Full-stack E-commerce Web Application project for my Database Application course at RMIT University Vietnam, in which I worked as the program manager, SCRUM Master, and lead database architect, aiding my team in timely releases of deliverable for each sprint, communication with the stakeholders, and supervision of the integration of our database, backend, and frontend. This has strengthen my skill to work both independently and in an collaborative team environment with a strong focus on communication with the stakeholders, critical thinking, adaptability, and independent problem solving.}

\p{Thank you for your time and consideration. I look forward to the opportunity to contribute and learn at Synopsys Vietnam.}

\p{Best regards,\\
Tuong-Minh (Mike) Vo}
%

\end{document}
% ============================================== %
